### 2016-02-18 ch02-qlogms/excitation-design.tex
Clean up figures from CH02

  \begin{figure}[ht]
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
    \label{fig:freqGrids}
  \end{figure}

@@

  \begin{figure}
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/misalign.tikz}
    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
    The $3\unit{dB}$ bandwidth (\sysBW) around the peak frequency $\wM$ of the system is highlighted.}
    \label{fig:misalignment-logms}
  \end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figureheight{5cm}
      \setlength\figurewidth{0.65\columnwidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment coefficient $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (cfr. \eqref{eq:optimAlpha}).}
    \label{fig:worstCaseBeta}
  \end{figure}

  Such signals are clearly undesirable, as a misalignment smaller than the grid spacing of the excitation grid and the system will entail a large increase in the uncertainty of estimate.

@@

  \begin{figure}[ht]
    \centering
      \setlength\figureheight{5cm}
      \setlength\figurewidth{0.65\columnwidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.
             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
    \label{fig:worstCaseAlpha}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figureheight{4cm}
      \setlength\figurewidth{0.7\columnwidth}
    \input{\thisDir/figs/SignalAndSystem.tikz}
    \caption[System with highlighted bandwidth and multisine components.]{Depiction of the transfer function $G$ of a second order system, along with a logarithmic multisine excitation $U$ for $\alpha = \alpha^{\star}$. The circled sine components lie within the $3 \unit{dB}$ bandwidth of $G$.}%
    \label{fig:signalAndSystem}
  \end{figure}

@@

  \begin{figure}[th]
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/Sys02-4.tikz}
    \caption[Simulated FRF and its variance for different excitation signals.]{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$
             along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
    \label{fig:FRF1}
  \end{figure}

@@

  \begin{figure}%
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption[Simulated FRFs and their variances of systems with $\damping=0.2$ for different excitation signals.]{FRFs for different second order systems with constant damping
             $\damping=0.2$ but different resonance frequencies. Comparison of the
             variances around the respective resonance frequency for the different
             excitation signals.}%
    \label{fig:damping02}
  \end{figure}

@@

  \begin{figure}%
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption[Simulated FRFs and their variances of systems with $\damping=0.05$ for different excitation signals.]{FRFs for different second order systems with constant damping
             $\damping=0.05$ but different resonance frequencies. Comparison of the
             variances around the respective resonance frequency for the different
             excitation signals.}%
    \label{fig:damping005}
  \end{figure}

@@

\begin{figure}%
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
           \TODO{also with other excitation signals?}
  \label{fig:sumSys}
\end{figure}

@@

    \begin{figure}%
    \centering
      \setlength\figureheight{5cm}
      \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
      \label{fig:measurements}
    \end{figure}

>>>>

  \begin{figure}[ht]
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/freqGrid.tikz}
    \caption[Amplitude spectrum for linear, logarithmic, quasi-logarithmic grids.]{Comparison of the amplitude spectrum of a linear grid multisine, a logarithmic grid multisine, the compensated quasi-logarithmic multisine and the `pink' quasi-log multisine.}%
    \label{fig:freqGrids}
  \end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/misalign.tikz}
    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
    The $3\unit{dB}$ bandwidth (\sysBW) around the peak frequency $\wM$ of the system is highlighted.}
    \label{fig:misalignment-logms}
  \end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment coefficient $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (cfr. \eqref{eq:optimAlpha}).}
    \label{fig:worstCaseBeta}
  \end{figure}

  Such signals are clearly undesirable, as a misalignment smaller than the grid spacing of the excitation grid and the system will lead to a large increase in the uncertainty of estimate.

@@

  \begin{figure}[ht]
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.
             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
    \label{fig:worstCaseAlpha}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.5\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/SignalAndSystem.tikz}
    \caption[System with highlighted bandwidth and multisine components.]{Depiction of the transfer function $G$ of a second order system, along with a logarithmic multisine excitation $U$ for $\alpha = \alpha^{\star}$. The circled sine components lie within the $3 \unit{dB}$ bandwidth of $G$.}%
    \label{fig:signalAndSystem}
  \end{figure}

@@

  \begin{figure}[th]
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/Sys02-4.tikz}
    \caption[Simulated FRF and its variance for different excitation signals.]{\gls{FRF}~\legref{leg:excitation:sim:FRF} of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.2$ along with the corresponding variance and bias of the parametric models obtained using three different kinds of multisine excitations.}%
    \label{fig:FRF1}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping02-cmp.tikz}
    \caption[Simulated FRFs and their variances of systems with $\damping=0.2$ for different excitation signals.]{\glspl{FRF} for different second order systems with constant damping
             $\damping=0.2$ but different resonance frequencies. Comparison of the
             variances around the respective resonance frequency for the different
             excitation signals.}%
    \label{fig:damping02}
  \end{figure}

@@

  \begin{figure}%
    \centering
      \setlength\figurewidth{0.68\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/damping005-cmp.tikz}
    \caption[Simulated FRFs and their variances of systems with $\damping=0.05$ for different excitation signals.]{FRFs for different second order systems with constant damping
             $\damping=0.05$ but different resonance frequencies. Comparison of the
             variances around the respective resonance frequency for the different
             excitation signals.}%
    \label{fig:damping005}
  \end{figure}

@@

\begin{figure}%
  \centering
  \setlength\figurewidth{0.68\columnwidth}
  \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
           \TODO{also with other excitation signals?}
  \label{fig:sumSys}
\end{figure}

@@

    \begin{figure}%
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/qlog_a050mall.tikz}
    \caption[Measured FRFs of all BK1613 octave filters and their variance for different excitation signals.]{Measured FRFs of the different \bruelkjaer BK1613 octave filters together with the observed variance for a linear, quasi-log and pink quasi-log grid multisine.}%
      \label{fig:measurements}
    \end{figure}
